Red-Giant Hot Jupiters: Brilliant Radio Beacons?

### 2015-06-01 ms.tex
scaling of radius of magnetic stand-off point is corrected
consideration of radio spectra

The radius of the magnetic stand-off point, $r_s$, is obtained based on the balance between the stellar wind pressure and the planetary magnetic pressure: 
%%%
\begin{equation}
m_p n v ^2 \sim \frac{B^2}{8\pi}\left( \frac{r_s}{R_p} \right)^{-6}  \label{eq:stand-off}
\end{equation}
%%%
The radius obtained for Jupiter from this equality is about a half of actual radius of Magnetosphere \citep[][]{griesmeier2005}. We estimate $r_s$ simply by scaling Jovian magnetosphere \citep[$r_{s,\,J} \sim 84 R_J$][]{joy2002} according to equation (\ref{eq:stand-off}), i.e., 
%%%
\begin{eqnarray}
r_s 
%&\sim & R_p \left( \frac{B^2}{8\pi m_{\rm p}nv^2} \right)^{1/6}  \\
&=& r_{s,\,J} \left( \frac{B}{10~\mbox{G}} \right)^{1/3} \left( \frac{\dot a}{5.2\mbox{AU}} \right)^{-1/3}  \\
&& \times \left( \frac{\dot M_\star}{\dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{v_{\odot }} \right)^{-1/6} \\
&=& 11.3 \, R_J \left( \frac{B}{10~\mbox{G}} \right)^{1/3}  \left( \frac{\dot a}{5\mbox{AU}} \right)^{-1/3} \\
&& \times \left( \frac{\dot M_\star}{10^6 \dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{10^{-1}v_{\odot }} \right)^{-1/6}
 \label{eq:stand-off-radius}
\end{eqnarray}
%%%

@@

Number of particle which is trapped by planetary magnetosphere is
\begin{equation}
n \propto \pi r_s^2
\end{equation}

>>>>

The radius of the magnetic stand-off point, $r_s$, is obtained based on the balance between the stellar wind pressure and the planetary magnetic pressure: 
%%%
\begin{equation}
m_p n v ^2 \sim \frac{B^2}{8\pi}\left( \frac{r_s}{R_p} \right)^{-6}  \label{eq:stand-off}
\end{equation}
%%%
The radius obtained for Jupiter from this equality is about a half of actual radius of Magnetosphere \citep[][]{griesmeier2005}. We estimate $r_s$ simply by scaling Jovian magnetosphere \citep[$r_{s,\,J} \sim 84 R_J$][]{joy2002} according to equation (\ref{eq:stand-off}), i.e., 
%%%
\begin{eqnarray}
r_s 
%&\sim & R_p \left( \frac{B^2}{8\pi m_{\rm p}nv^2} \right)^{1/6}  \\
&=& r_{s,\,J} \left( \frac{B}{10~\mbox{G}} \right)^{1/3} \left( \frac{a}{5.2\mbox{AU}} \right)^{1/3}  \\
&& \times \left( \frac{\dot M_\star}{\dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{v_{\odot }} \right)^{-1/6} \\
&=& 11.3 \, R_J \left( \frac{B}{10~\mbox{G}} \right)^{1/3}  \left( \frac{a}{5\mbox{AU}} \right)^{1/3} \\
&& \times \left( \frac{\dot M_\star}{10^6 \dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{10^{-1}v_{\odot }} \right)^{-1/6}
 \label{eq:stand-off-radius}
\end{eqnarray}
%%%

@@

The cyclotron frequency at radius $r$ is:
%%%
\begin{equation}
f_{\rm cyc} = \frac{e B(r)}{2\pi m_e} \propto \frac{B_p}{r^3}
\end{equation}
%%
Therefore, 
%%%
\begin{equation}
\frac{dP}{df_{\rm cyc}} = \frac{dP}{d\nu } \propto -\frac{r^4}{B_p} \frac{dP}{dr}
\end{equation}
%%%
Employing Larmor formula, power emitted from a thin shell at $r\sim r+dr$, $dP/dr$ is 
%%%
\begin{equation}
\frac{dP}{dr} \propto 4\pi r^2 N_{\rm plasma}(r) v_{\bot }^2(r) B^2(r) \label{eq:larmor}
\end{equation}
%%%
where $N_{\rm plasma}(r) $ represents the number density of plasma in the planetary magnetosphere at radius $r$.

We assume that $N_{\rm plasma}(r_s) $  is proportional to the squared radius of the magnetic stand-off point:
%%%
\begin{equation}
N_{\rm plasma}(r_s) \propto \pi r_s^2 \;\;(\propto B_p^{2/3}) \label{eq:N0_plasma}
\end{equation}
%%%
Due the the mass flux conservation,
%%%
\begin{equation}
4 \pi r^2 N_{\rm plasma}(r) v_{\|} = const.
\end{equation}
%%%
Combining with equation (\ref{eq:N0_plasma}),
%%%
\begin{equation}
N_{\rm plasma}(r) \propto  r_s^2 \frac{v_{\|}(r)}{r^2} \propto  B_p^{2/3} \cdot \frac{v_{\|}(r)}{r^2}
\end{equation}
%%%

Because the magnetic dipole moment
%%%
\begin{equation}
\mu = \frac{mv_{\bot}(r)}{eB(r)}
\end{equation}
%%%
is approximately to be constant while the plasma falls down along the magnetic field, 
%%%
\begin{eqnarray}
v_{\bot }(r) \propto \frac{1}{r^3} \label{eq:v_bot} \\
B(r) \propto \frac{B_p}{r^3} 
\end{eqnarray}
%%%
On the other hand, conservation of energy ensures that
%%%
\begin{equation}
\mathcal{E} = -\frac{GM_p}{r} + \frac{v_{\bot }^2}{2} + \frac{v_{\|}^2}{2}=const.
\end{equation}
%%%
Assuming that the initial energy (at $r=r_s$) is negligible compared to those near the surface, $\mathcal{E}=0$, 
%%%
\begin{equation}
v_{\|}^2 \sim \frac{GM_p}{r} - \frac{v_{\bot ,0}^2}{2} \left( \frac{r}{r_s} \right)^{-6} \label{eq:v_||}
\end{equation}
%%%

Substituting equations (\ref{eq:N0_plasma}),  (\ref{eq:v_bot}) and (\ref{eq:v_||}) into equation (\ref{eq:larmor}) leads to
%%%
\begin{equation}
\frac{dP}{dr} \propto \frac{B_p^{8/3}}{r^{12}} \left( \frac{GM_p}{r} - \frac{v_{\bot ,0}^2}{2} \left( \frac{r}{r_s} \right)^{-6} \right)^{1/2}  
\end{equation}
%%%
The right-hand side has the maximum value $\sqrt{5GM_p/6\tilde r} $ at radius $\tilde r=(6v_{\bot ,0}^2/GM_p)^{1/5}$. 
At $r>>\tilde r$, 
%%%
\begin{equation}
\frac{dP}{dr} \propto \frac{B_p^{8/3}}{r^{25/2}}
\end{equation}
%%%
and
%%%
\begin{equation}
\frac{dP}{d\nu } \propto \frac{B_p^{5/3}}{r^{17/2}} \propto \frac{\nu^{17/6}}{B_p^{7/6}}
\end{equation}
%%%

At $r<<\tilde r$, 
%%%
\begin{equation}
\frac{dP}{dr} \propto \frac{B_p^{8/3}}{r^{15}}
\end{equation}
%%%
and
%%%
\begin{equation}
\frac{dP}{d\nu } \propto \frac{B_p^{5/3}}{r^{11}} \propto \frac{\nu^{11}}{B_p^{28/3}}
\end{equation}
%%%
